---
title: "RMD-Example 1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)

latexImg = function(latex){

    link = paste0('http://latex.codecogs.com/gif.latex?',
           gsub('\\=','%3D',URLencode(latex)))

    link = gsub("(%..)","\\U\\1",link,perl=TRUE)
    return(paste0('![](',link,')'))
} ## geklaut von https://github.com/STAT545-UBC/Discussion/issues/102#issuecomment-142482040
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated. `r latexImg('a = \\frac{b}{c}')`

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
as.tibble(cars) %>% 
  ggplot(aes(x=speed, y=dist))+
  geom_point()

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
